---
title: "Specify the model to use"
execute:
  eval: true
  freeze: true
---

```{r}
#| include: false
source("../site/knitr-print.R")
```

[R/llm-use.R](https://github.com/mlverse/mall/blob/main/r/R/llm-use.R)

## llm_use

## Description
Allows us to specify the back-end provider, model to use during the current R session


## Usage
```r

llm_use(
  backend = NULL,
  model = NULL,
  ...,
  .silent = FALSE,
  .cache = NULL,
  .force = FALSE
)
```

## Arguments
|Arguments|Description|
|---|---|
| backend | "ollama" or an `ellmer` `Chat` object. If using "ollama", `mall` will use is out-of-the-box integration with that back-end. Defaults to "ollama". |
| model | The name of model supported by the back-end provider |
| ... | Additional arguments that this function will pass down to the integrating function. In the case of Ollama, it will pass those arguments to `ollamar::chat()`. |
| .silent | Avoids console output |
| .cache | The path to save model results, so they can be re-used if the same operation is ran again. To turn off, set this argument to an empty character: `""`. It defaults to a temp folder. If this argument is left `NULL` when calling this function, no changes to the path will be made. |
| .force | Flag that tell the function to reset all of the settings in the R session |



## Value
A `mall_session` object


## Examples
```{r}


library(mall)

llm_use("ollama", "llama3.2")

# Additional arguments will be passed 'as-is' to the
# downstream R function in this example, to ollama::chat()
llm_use("ollama", "llama3.2", seed = 100, temperature = 0.1)

# During the R session, you can change any argument
# individually and it will retain all of previous
# arguments used
llm_use(temperature = 0.3)

# Use .cache to modify the target folder for caching
llm_use(.cache = "_my_cache")

# Leave .cache empty to turn off this functionality
llm_use(.cache = "")

# Use .silent to avoid the print out
llm_use(.silent = TRUE)

# Use an `ellmer` object
library(ellmer)
chat <- chat_openai(model = "gpt-4o")
llm_use(chat)



```


