---
title: "Extract entities from text"
execute:
  eval: true
  freeze: true
---

```{r}
#| include: false
source("../utils/knitr-print.R")
```

[R/llm-extract.R](https://github.com/mlverse/mall/blob/main/R/llm-extract.R)

## llm_extract

## Description
 Use a Large Language Model (LLM) to extract specific entity, or entities, from the provided text 


## Usage
```r
 
llm_extract( 
  .data, 
  col, 
  labels, 
  expand_cols = FALSE, 
  additional_prompt = "", 
  pred_name = ".extract" 
) 
 
llm_vec_extract(x, labels = c(), additional_prompt = "", preview = FALSE) 
```

## Arguments
|Arguments|Description|
|---|---|
| .data | A `data.frame` or `tbl` object that contains the text to be analyzed |
| col | The name of the field to analyze, supports `tidy-eval` |
| labels | A vector with the entities to extract from the text |
| expand_cols | If multiple `labels` are passed, this is a flag that tells the function to create a new column per item in `labels`. If `labels` is a named vector, this function will use those names as the new column names, if not, the function will use a sanitized version of the content as the name. |
| additional_prompt | Inserts this text into the prompt sent to the LLM |
| pred_name | A character vector with the name of the new column where the prediction will be placed |
| x | A vector that contains the text to be analyzed |
| preview | It returns the R call that would have been used to run the prediction. It only returns the first record in `x`. Defaults to `FALSE` Applies to vector function only. |



## Value
 `llm_extract` returns a `data.frame` or `tbl` object. `llm_vec_extract` returns a vector that is the same length as `x`. 


## Examples
```{r}
 
library(mall) 
 
data("reviews") 
 
llm_use("ollama", "llama3.2", seed = 100, .silent = TRUE) 
 
# Use 'labels' to let the function know what to extract 
llm_extract(reviews, review, labels = "product") 
 
# Use 'pred_name' to customize the new column's name 
llm_extract(reviews, review, "product", pred_name = "prod") 
 
# Pass a vector to request multiple things, the results will be pipe delimeted 
# in a single column 
llm_extract(reviews, review, c("product", "feelings")) 
 
# To get multiple columns, use 'expand_cols' 
llm_extract(reviews, review, c("product", "feelings"), expand_cols = TRUE) 
 
# Pass a named vector to set the resulting column names 
llm_extract( 
  .data = reviews, 
  col = review, 
  labels = c(prod = "product", feels = "feelings"), 
  expand_cols = TRUE 
) 
 
# For character vectors, instead of a data frame, use this function 
llm_vec_extract("bob smith, 123 3rd street", c("name", "address")) 
 
# To preview the first call that will be made to the downstream R function 
llm_vec_extract( 
  "bob smith, 123 3rd street", 
  c("name", "address"), 
  preview = TRUE 
) 
 
```


