---
title: "Send a custom prompt to the LLM"
execute:
  eval: true
  freeze: true
---

```{r}
#| include: false
source("../utils/knitr-print.R")
```

[R/llm-custom.R](https://github.com/edgararuiz/mall/blob/main/R/llm-custom.R)

## llm_custom

## Description
 Use a Large Language Model (LLM) to process the provided text using the instructions from `prompt` 


## Usage
```r
 
llm_custom(.data, col, prompt = "", pred_name = ".pred", valid_resps = "") 
 
llm_vec_custom(x, prompt = "", valid_resps = NULL) 
```

## Arguments
|Arguments|Description|
|---|---|
| .data | A `data.frame` or `tbl` object that contains the text to be analyzed |
| col | The name of the field to analyze, supports `tidy-eval` |
| prompt | The prompt to append to each record sent to the LLM |
| pred_name | A character vector with the name of the new column where the prediction will be placed |
| valid_resps | If the response from the LLM is not open, but deterministic, provide the options in a vector. This function will set to `NA` any response not in the options |
| x | A vector that contains the text to be analyzed |



## Value
 `llm_custom` returns a `data.frame` or `tbl` object. `llm_vec_custom` returns a vector that is the same length as `x`. 


## Examples
```{r}
 
library(mall) 
 
llm_use("ollama", "llama3.1", seed = 100, .silent = TRUE) 
 
reviews <- data.frame(review = c( 
  "This has been the best TV I've ever used. Great screen, and sound.", 
  "I regret buying this laptop. It is too slow and the keyboard is too noisy", 
  "Not sure how to feel about my new washing machine. Great color, but hard to figure" 
)) 
 
my_prompt <- paste( 
  "Answer a question.", 
  "Return only the answer, no explanation", 
  "Acceptable answers are 'yes', 'no'", 
  "Answer this about the following text, is this a happy customer?:" 
) 
 
reviews |> 
  llm_custom(review, my_prompt) 
 
  
```


