---
title: "Sentiment analysis"
execute:
  eval: true
  freeze: true
---

```{r}
#| include: false
source("../utils/knitr-print.R")
```

[R/llm-sentiment.R](https://github.com/mlverse/mall/blob/main/R/llm-sentiment.R)

## llm_sentiment

## Description
 Use a Large Language Model (LLM) to perform sentiment analysis from the provided text 


## Usage
```r
 
llm_sentiment( 
  .data, 
  col, 
  options = c("positive", "negative", "neutral"), 
  pred_name = ".sentiment", 
  additional_prompt = "" 
) 
 
llm_vec_sentiment( 
  x, 
  options = c("positive", "negative", "neutral"), 
  additional_prompt = "", 
  preview = FALSE 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| .data | A `data.frame` or `tbl` object that contains the text to be analyzed |
| col | The name of the field to analyze, supports `tidy-eval` |
| options | A vector with the options that the LLM should use to assign a sentiment to the text. Defaults to: 'positive', 'negative', 'neutral' |
| pred_name | A character vector with the name of the new column where the prediction will be placed |
| additional_prompt | Inserts this text into the prompt sent to the LLM |
| x | A vector that contains the text to be analyzed |
| preview | It returns the R call that would have been used to run the prediction. It only returns the first record in `x`. Defaults to `FALSE` Applies to vector function only. |



## Value
 `llm_sentiment` returns a `data.frame` or `tbl` object. `llm_vec_sentiment` returns a vector that is the same length as `x`. 


## Examples
```{r}
 
library(mall) 
 
data("reviews") 
 
llm_use("ollama", "llama3.2", seed = 100, .silent = TRUE) 
 
llm_sentiment(reviews, review) 
 
# Use 'pred_name' to customize the new column's name 
llm_sentiment(reviews, review, pred_name = "review_sentiment") 
 
# Pass custom sentiment options 
llm_sentiment(reviews, review, c("positive", "negative")) 
 
# Specify values to return per sentiment 
llm_sentiment(reviews, review, c("positive" ~ 1, "negative" ~ 0)) 
 
# For character vectors, instead of a data frame, use this function 
llm_vec_sentiment(c("I am happy", "I am sad")) 
 
# To preview the first call that will be made to the downstream R function 
llm_vec_sentiment(c("I am happy", "I am sad"), preview = TRUE) 
 
```


