---
title: "Summarize text"
execute:
  eval: true
  freeze: true
---

```{r}
#| include: false
source("../utils/knitr-print.R")
```

[R/llm-summarize.R](https://github.com/edgararuiz/mall/blob/main/R/llm-summarize.R)

## llm_summarize

## Description
 Use a Large Language Model (LLM) to summarize text 


## Usage
```r
 
llm_summarize( 
  .data, 
  col, 
  max_words = 10, 
  pred_name = ".summary", 
  additional_prompt = "" 
) 
 
llm_vec_summarize(x, max_words = 10, additional_prompt = "", preview = FALSE) 
```

## Arguments
|Arguments|Description|
|---|---|
| .data | A `data.frame` or `tbl` object that contains the text to be analyzed |
| col | The name of the field to analyze, supports `tidy-eval` |
| max_words | The maximum number of words that the LLM should use in the summary. Defaults to 10. |
| pred_name | A character vector with the name of the new column where the prediction will be placed |
| additional_prompt | Inserts this text into the prompt sent to the LLM |
| x | A vector that contains the text to be analyzed |
| preview | It returns the R call that would have been used to run the prediction. It only returns the first record in `x`. Defaults to `FALSE` Applies to vector function only. |



## Value
 `llm_summarize` returns a `data.frame` or `tbl` object. `llm_vec_summarize` returns a vector that is the same length as `x`. 


## Examples
```{r}
 
library(mall) 
 
data("reviews") 
 
llm_use("ollama", "llama3.1", seed = 100, .silent = TRUE) 
 
# Use max_words to set the maximum number of words to use for the summary 
llm_summarize(reviews, review, max_words = 5) 
 
# Use 'pred_name' to customize the new column's name 
llm_summarize(reviews, review, 5, pred_name = "review_summary") 
 
# For character vectors, instead of a data frame, use this function 
llm_vec_summarize( 
  "This has been the best TV I've ever used. Great screen, and sound.", 
  max_words = 5 
) 
 
# To preview the first call that will be made to the downstream R function 
llm_vec_summarize( 
  "This has been the best TV I've ever used. Great screen, and sound.", 
  max_words = 5, 
  preview = TRUE 
) 
 
```


